---
title: "Xeva Tutorial"
author: "Arvind Mer"
date: "`r Sys.Date()`"
output: 
  pdf_document
vignette: >
  %\VignetteIndexEntry{Introduction to the Xeva R package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{style-knitr, eval=TRUE, echo=FALSE, results="asis"}
BiocStyle::latex()
```

The Xeva package provides efficient and powerfull functions for patient drived xenograft (PDX) based pharmacogenomic data analysis. 

Load Xeva library and PDXE breast cancer dataset
```{r load, echo=TRUE}
library(Xeva)
data(brca)
brca
```
To store and access the data **Xeva** uses `r class(brca)[1]` class. 
**Xeva** stores data for each individual PDX model. We can see the infromation about models as
```{r, echo=TRUE, tidy=TRUE}
brca.mod <- modelInfo(brca)
head(brca.mod)
```

Create the mRECIST plot for data
```{r, echo=TRUE, tidy=TRUE}
brca.mr <- summarizeResponse(brca, response.measure = "mRECIST")
head(brca.mr)
plotmRECIST(brca.mr, control.name = "untreated")
```

Plot PDX curve for a drug
```{r, echo=TRUE, tidy=TRUE}
plotBatch(brca, batch = "X-4567.BKM120")

plotBatch(brca, patient.id="X-4567", drug="BKM120", control.name="untreated")

```

